This chapter contains a description of the implementation of the project's server side. This chapter will describe the
structure of the project. It is intended to familiarize the reader with the implementation of this application and to
simplify the understanding of the structure of the project for future developers.

Note that installation guide for this application is in the attachments.


\newcommand{\appitem}[1]{
\item\textbf{#1}.
}
\newcommand{\setitem}[1]{
\item\textbf{#1}.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Django project structure %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Project structure}
Django as a framework determines the structure of the whole system. Django project is divided into logical parts - apps.
Apps contain a set of modules with classes, that implement interfaces and extend classes, that are provided by Django.

Later in this section, the main modules of the apps in the Django project will be described. The parts involved in
processing of the request for the receiving of the user's wishes, will be taken as an example.

\subsection{Django models}
Django models is an interface for simplified querying to database. All models extend class \class{model} from
\module{django.db} module and usually represent single table in a database \cite{djangodocs}.

Thus, each app except the feed and notifications contains a module \module{models}. In this module there are models that
completely describe the database. Despite what kind of DBMS is used (PostgreSQL or SQLite) the Django models and quering
through them does not change, which simplifies development, testing and deploy.

Model that represent table \class{Wish} in the database:
\begin{lstlisting}
class Wish(models.Model):
    title = models.CharField(max_length=100)
    description = models.CharField(max_length=512)
    amount_needed = models.FloatField()
    date_created = models.DateTimeField(auto_now_add=True)
    date_of_expiration = models.DateTimeField(null=True)
    date_completed = models.DateTimeField(null=True)
    is_public = models.BooleanField(default=False)
    author = models.ForeignKey(User,
                               on_delete=models.CASCADE,
                               related_name='wishes')

    class Meta:
        db_table = 'Wish'

\end{lstlisting}

\subsection{Django views}
Django view is a method that is called during request on certain \ac{URL}. This function takes a Web request and returns
a Web response, in this case JSON. The main logic of processing requests is in the views.

Before we started using Django REST framework, the request on receiving the wish list of the current user looked like
this:
\begin{lstlisting}
def current_user_wishes_view(request):
    current_user = request.user
    if not user.is_authenticated():
        return HttpResponse('Unauthorized', status=401)

    current_user_wishes = current.user.wishes. \
                                     order_by('-date_created')

    response_data = []
    for wish in current_user_wishes:
        serialized_wish = WishSerializer(wish).data
        response_data.append(serialized_wish)

    paginated_response = WishPagination(). \
               get_paginated_response(request, response_data)

    return JsonResponse(paginated_response)

\end{lstlisting}
Similar requests to obtain a list of objects of a certain model (wishes, donations, comments, etc.) look very similar.
It is checked if the user is authenticated, the data queryset is obtained, the data is serialized, paginated (divided
into pages), returned in the \ac{JSON} format. To simplify the implementation of such requests and the corresponding
auxiliary classes (serializers, paginations, etc.), it was decided to use the Django REST framework.

Thus, in Django REST framework view on getting the current user's wish list looks like this:

\begin{lstlisting}
class CurrentUserWishesView(generics.ListCreateAPIView):
    renderer_classes = (renderers.JSONRenderer,)
    permission_classes = (permissions.IsAuthenticated,)
    serializer_class = serializers.WishSerializer
    pagination_class = pagination.WishPagination

    def get_queryset(self):
        user = self.request.user
        return user.wishes.order_by('-date_created')
\end{lstlisting}

This approach simplifies implementation and improves the readability of the code.


\subsection{Django urls}
The \module{urls} module in Django is responsible for linking the \ac{URL} endpoints to their corresponding views. It
contains a list of objects \class{url}. In \app{wishes} app it looks like this:

\begin{lstlisting}
urlpatterns = [
    url(r'wishes/', CurrentUserWishesView.as_view()),
    # other urls
]
\end{lstlisting}


\subsection{Django REST serializers}
Django REST serializers is an interface that provides the Django REST framework for simplifying the serialization and
desirilization of instances of Django models. The simplest wish serializer looks like this:
\begin{lstlisting}
class WishSerializer(serializers.ModelSerializer):
    class Meta:
        model = Wish
        fields = '__all__'
        read_only_fields = ('id', 'author', 'date_created',
                            'date_completed', 'amount_gathered',
                            'donators_count')
\end{lstlisting}


\subsection{Django REST pagination}
To avoid large responses in the case of a large number of objects in the queryset, it was decided to use pagination.
Pagination is the partitioning of the response into so-called pages of the same size. To create a class responsible for
the pagination of the list of data, it is enough to extend the \class{PageNumberPagination} class from the module
\module{rest\_framework.pagination}:

\begin{lstlisting}
class WishPagination(PageNumberPagination):
    page_size = 10
    page_size_query_param = 'page_size'
    max_page_size = 50
\end{lstlisting}

If this class is used as \field{pagination\_class} in the view, \field{page\_size} and \field{page} are used in the
\ac{URL} as optional parameters. So on the request "/wishes?page\_size=5\&page=2" server will respond with \ac{JSON} in
following format:

\begin{lstlisting}
{
  "count": 13,
  "next": "https://api.elateme.com/wishes?page_size=5&page=3",
  "previous": "https://api.elateme.com/wishes?page_size=5&page=1",
  "results": [
    # 5 serialized wishes from the second page
  ]
}
\end{lstlisting}


\subsection{Django apps}
The project was divided into the following apps:

\begin{itemize}

\appitem{account} This app includes modules for storing and processing information about the user. \app{account} is
divided into sub-applications \app{authorization} and \app{social} that are responsible for user authorization and
integration with social networks respectively.
\appitem{donations} This app is designed to process donations. It will also contain the logic of the payment and refund
systems.
\appitem{feed} App for the arrangement of a user's news feed.
\appitem{friendship} Application for the processing of friendly relationships between users.
\appitem{notifications} App provids user notifications. At the moment, it provides the REST interface for getting news
list. Later this application will work with push-notifications.
\appitem{wishes} Application provids interface for processing user wishes. It also contains sub-application \app{comments}.

\end{itemize}

\subsection{Django settings}
Django \module{settings} is a module that contains all the configuration of the Django project. The main configurations
to notice are:

\begin{itemize}
    \setitem{INSTALLED\_APPS} A list of all apps in a project.
    \setitem{ALLOWED\_HOSTS} A list of the host/domain names that this Django site can serve.
    \setitem{DATABASES} A dictionary containing the settings for all databases to be used with Django.
    \setitem{DEBUG} A boolean that turns on/off debug mode.
\end{itemize}

Complete list of settings available in Django can be found in the oficial documetation \cite{djangosettings}.

As for development and deployment it is needed to have different configuratiouns for allowed hosts, databases and
debuging, in the \file{server\_api} folder, alongside with \module{setting} module there were created two modules:
\module{prod\_settings} and \module{dev\_settings}. They contain specific configurations for production and development
respectively. For example \module{dev\_settings} have configured SQLite database and set debug mode while
\module{prod\_settings} defines settings for PostgreSQL and without debug mode. To enable \module{prod\_settings} it is
needed to set environment variable \textit{PRODUCTION}. Otherwise \module{dev\_settings} will be used.

Following lines were added to the main \module{settings} module to make it work:

\begin{lstlisting}
if os.environ.get('PRODUCTION', False):
    from .prod_settings import *
else:
    from .dev_settings import *
\end{lstlisting}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Python Virtual Environment %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Python Virtual Environment}
Since this application uses a set of dependencies that don’t come as part of the python standard library they must be
installed for all instances of the application, namely the development and testing on the local machines of developers
and on the production server. Python Virtual Environment was used for these purposes.

A Virtual Environment is a tool to keep the dependencies required by different projects in separate places, by
creating virtual Python environments for them. It solves the “Project X depends on version 1.x but, Project Y
needs 4.x” dilemma, and keeps your global site-packages directory clean and manageable.\cite{pythonvenv}

A list of all the dependencies that are installed in the virtual environment can be found in the \file{requirements.txt}
file in the project's root directory. The guide for installing and configuring the virtual environment is described in
the installation guide in the attachments.
