The aim of this work was to learn how to develop a complex backend system from the analysis of the requirements and the design of the future system to implementation, deploy and testing. Functional and non-functional requirements, use cases and business processes were documented. The structure of the project, the scheme of the database and the class model, the payment and refund systems were designed, REST API for communication with mobile and web applications was implemented and the implemented application was tested by the unit and performance tests.

In the framework of this thesis, the author studied the use of such web development tools like Python, Django and Django REST frameworks, Nginx and PostgreSQL. The author also learned about ways to integrate user authorization via Facebook using OAuth 2.0 protocol and payment systems like FIO-Bank and Bitcoins.


\section{Work contribution}
The reader of this work can learn for himself how to implement the authorization system through the OAuth 2.0 protocol, the basics of using the interfaces of the FIO-banks and the Bitcoin payment systems. Also, the work explains the structure of the implementation of this project, which will be useful for future developers of this platform.

\section{Future outlook}
The next step in developing of the backend of the application will be the completion of the REST API and the integration with the advert server. Also, it will be necessary to study in detail the configurations of the Nginx and ways to optimize the server and perform performance testing on the production server.
